### 2019-01-07 writing/thesis/chapters/results.tex
Small fix?

We use a single node of the Haswell-nodes of the Supermuc (Phase 2).
The node has two xxx\todo{name cpus} \textsc{cpu}s with 28 cores each.
Both \textsc{cpu}s currently run on \SI{1.8}{\GHz}
We use the \tbb{} parallelisation of \exahype{}.
To find a reasonable parameter for the number of background threads, we ran a grid search.
We ran three \amr{} testcases for a simulation time of \SI{1}{\min}.
\todo{Noisy, show results}
The best median performance was achieved by using seven background threads.

>>>>

We use a single node of the Haswell-nodes of the Supermuc (Phase 2).
The node has two xxx\todo{name cpus} \textsc{cpu}s with 28 cores each.
Both \textsc{cpu}s currently run on $\SI{1.8}{\GHz}$.
We use the \tbb{} parallelisation of \exahype{}.
To find a reasonable parameter for the number of background threads, we ran a grid search.
We ran three \amr{} testcases for a simulation time of $\SI{1}{\min}$.
\todo{Noisy, show results}
The best median performance was achieved by using six background threads.
